### 2021-04-08 papers/SYRCoSE/future.tex

First, we plan to apply our library to a wider range of problems. 
We are going to develop a mechanised semantics of some classical 
languages used to model concurrency, in particular 
the calculus of communicating systems~(CCS)~\cite{Milner:80} and 
$\pi$-calculus~\cite{Milner:99}.      
We also plan to continue our work on 
expressing various relaxed models 
of shared memory~\cite{Lahav-al:POPL16, Lahav-al:PLDI17, Podkopaev-al:POPL19}
in terms of event structures.

>>>>

First, we plan to apply our library to a wider range of problems. 
We are going to develop a mechanised semantics of some long-established
languages used to model concurrency, in particular 
the calculus of communicating systems~(CCS)~\cite{Milner:80} and 
$\pi$-calculus~\cite{Milner:99}.      
We also plan to continue our work on 
expressing various relaxed models 
of shared memory~\cite{Lahav-al:POPL16, Lahav-al:PLDI17, Podkopaev-al:POPL19}
in terms of event structures.

### 2021-04-08 papers/SYRCoSE/regmachine-eventstruct.tex

First, we need to show that $\caOrd \ \defeq \ (\lPO \cup \lRF)^*$
is a partial order. Reflexivity and transitivity follows immediately 
from the definition of the reflexive-transitive closure. 
To show antisymmetry note that $\lessdot_{\lPO} \subseteq \identOrd$
and $\lessdot_{\lRF} \subseteq \identOrd$ by construction. 
Therefore $\caOrd \subseteq \identOrd$. Since $\identOrd$ is
partial order, it is antisymmetric, and thus $\caOrd$ should also be antisymmetric.
The axiom of finite cause, \ie $\prefix{e}$ is finite for every event $e$, 
follows from the fact that at each step of the construction 
the set of possible predecessors of the new event 
can be over-approximated by the finite sequence $\eventSeq$.

@@

In \cref{fig:eventstruct-example} one can see the prime event structure
obtained as a result of incremental construction 
depicted in \cref{fig:regmachine-eventstruct-example}.

>>>>

First, we need to show that $\caOrd \ \defeq \ (\lPO \cup \lRF)^*$
is a partial order. Reflexivity and transitivity follows immediately 
from the definition of the reflexive-transitive closure. 
To show antisymmetry note that $\lessdot_{\lPO} \subseteq \identOrd$
and $\lessdot_{\lRF} \subseteq \identOrd$ by construction. 
Therefore $\caOrd \subseteq \identOrd$. Since $\identOrd$ is
a partial order, it is antisymmetric, and thus $\caOrd$ should also be antisymmetric.
The axiom of finite cause, \ie $\prefix{e}$ is finite for every event $e$, 
follows from the fact that at each step of the construction 
the set of possible predecessors of the new event 
can be over-approximated by the finite sequence $\eventSeq$.

@@

In \cref{fig:eventstruct-example} one can see the prime event structure
obtained as a result of the incremental construction 
depicted in \cref{fig:regmachine-eventstruct-example}.
